---
title: "Tessellation README"
output:
  pdf_document: default
  html_document: default
date: "2023-01-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abrupt-Abrupt Simulate Data

The simulated twenty abrupt-abrupt time series begins with creating a matrix ($20 \times 2$). Each row in the matrix will be used to determine the $\phi$ values for the simulated time series. The plot below shows this matrix. This matrix is used as a "Lookup Table" for the parameters in generating these time series.

```{r, echo = FALSE, message = FALSE}
source("SetUpSim1.R")

plot(xx, main = "'Look-Up Table Plot'")

```

The following explains how the data for the abrupt-abrupt simulated data is generated. The first set of time series below were created by using an AR(1) model with $\phi = 0.3$ for the first 500 time points and then combined with an AR(1) model with $\phi = -0.5$ for the last 500 time points.

```{r, message = FALSE, echo = FALSE}
source("SetUpSim1.R")
par(mfrow = c(2,3), mar = c(4.5,2.5,3,.2), las = 1)


ts.plot(x_t[,1])
ts.plot(x_t[,2])
ts.plot(x_t[,3])
ts.plot(x_t[,4])
ts.plot(x_t[,5])

mtext("AR(1), \U03D5 = 0.3 and \U03D5 = -0.5", outer = TRUE, line = -2)

```








